%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

  \textbf{{\LARGE Andrej Vyšný}} \\

  \textbf{Email:} \href{mailto:vysnyandrej@gmail.com}{vysnyandrej@gmail.com} 
  & \textbf{Linkedin:} \href{https://linkedin.com/in/andrejvysny}{https://linkedin.com/in/andrejvysny} \\
  
  \textbf{Mobil:} \href{tel:+421907323294}{+421 907 323 294} 
  & \textbf{Github:} \href{https://github.com/andrejvysny}{https://github.com/andrejvysny} \\


  & \textbf{Devpost:} \href{https://devpost.com/andrejvysny}{https://devpost.com/andrejvysny}\\
  
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
   	    
    \resumeSubheading
      {Slovak University of Technology}{Bratislava, Slovakia}
      %{Faculty of Electrical Engineering and Information Technology }{2021 - present}
      {Bachelor of Robotics and Cybernetics; Bachelor's Thesis: Robotic Stock-Keeper  }{2021 - present}  

    \resumeSubheading
      %{Základná Umelecká Škola Ľudovíta Fullu}{Ružomberok, Slovakia}
      {Art School of Ľudovít Fulla}{Ružomberok, Slovakia}
      {First Level, Second Level - Drawing, Painting, Woodcarving, Design  }{2007 - 2019}  
  
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Programming Languages}{PHP, JavaScript, Python, SQL, Bash, C/C++ }
	\resumeSubItem{Technologies }{Symfony, Laravel, React.js, Ionic, Docker, Github Actions, ROS}
    \resumeSubItem{Platforms }{Github, Microsoft Azure, Websupport Hosting}
    
    \resumeSubItem{Programs }{Adobe Photoshop, Adobe Premiere Pro, Adobe After Effects, Fusion 360, Matlab}  

\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
    {Websupport s. r. o. }{Bratislava, Slovakia}
    {Junior PHP Developer - Intern}{January 2022 - present}
    \resumeItemListStart
    \resumeItem{Laravel and Symfony applications}{}
    \begin{description}[font=$\bullet$]
    \item {I am part of a team that was developing large internal applications. My main focus is on the backend side of the application. }
    \item {For some time I was part of BugFix team - fixing reported bugs across systems. }
    \item {The main focus of my work is refactoring legacy code to new.}
    \end{description}
    \resumeItemListEnd

  
    \resumeSubheading
    {Enimo s. r. o. }{Ružomberok, Slovakia}
    {Junior Fullstack Web Developer}{october 2019 - november 2020}
    \resumeItemListStart
    \resumeItem{Symfony web applications}{}
    \begin{description}[font=$\bullet$]
    \item {I was part of a team that was developing web applications such as portfolios or managing systems for many customers. My focus was on both, backend and frontend side of the application. Personally I have handeled some smaller projects and contributed on larger systems.}
    \end{description}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart


\resumeSubItem{CapturePoint.sk}{}
\resumeItemListStart
    \resumeItem{Description}{A travel web and app platform featuring a selection of visit-worthy locations with detailed information and a user-friendly global map for easy exploration.}
    \resumeItem{Link}{\href{https://www.capturepoint.sk}{https://www.capturepoint.sk}}
    \resumeItem{Technologies}{Symfony, Api Platform, Docker, MariaDB, React.js, Ionic, Github Actions}
    \resumeItem{Detailed description}{\href{https://devjourney.capturepoint.sk/}{https://devjourney.capturepoint.sk/}}
    %\resumeItem{Detailed project description}{}
\resumeItemListEnd


\resumeSubHeadingListEnd
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]

\item Winner of the Deutsche Telekom IT-Solutions Challenge at HackKosice 2024 - April 2024.
\item {The best technical solution - HackKosice 2023 - April 2023.} 
\item {2nd Place at the HackKosice 2022 Hackathon, Bloomreach Recommendation Challenge - April 2022.}

\end{description}
%-------------------------------------------



%-----------Certifications-----------------
%\section{Licenses and certifications}
%\begin{description}[font=$\bullet$]

%\item {Microsoft Azure Fundamentals AZ-900 - August, 2021}

%\end{description}
%-------------------------------------------


\end{document}